---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  collapse = TRUE,
  dpi = 600,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# calibratr
<!-- badges: start -->
<!-- badges: end -->

The goal of calibratr is to provide additional performance/calibration metrics and features for use within
the {yardstick} package in R. The included functions enable evaluation of model
performance from predictive models developed using the {tidymodels}
framework.

## Installation

You can install the development version of calibratr from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mglev1n/calibratr")
```

## Examples

Calculate brier score using the `two_class_example` dataset from `{yardstick}`:
```{r}
library(calibratr)
library(yardstick)

yardstick::two_class_example %>%
  brier(truth = truth, estimate = Class1)
```

Calculate scaled brier score using the `two_class_example` dataset from {yardstick}:
```{r}
library(calibratr)
library(yardstick)

yardstick::two_class_example %>%
  sbrier(truth = truth, estimate = Class1)
```

Calibration plot using the `two_class_example` dataset from {yardstick}:
```{r}
library(calibratr)
library(yardstick)
library(ggplot2)

yardstick::two_class_example %>%
  calib_curve(truth = truth, estimate = Class1) %>%
  autoplot()
```
